Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-08 tensor/draft/draft-tensor-op.tex
[draft] add note to describe Monte Carlo method

\begin{figure*}
  \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_0,2}
  \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_1,3}
  \caption{
    \eos{
    Constraints on real-valued [left] and complex-valued [right] scalar couplings
    $\wilson{S,\,S'}$ in the scenario SM-EFT from only $\overline{\cal B}(B_s \to
    \bar\mu\mu)$ (blue) and all data in \reftab{tab:observables} (green)
    at 68\% (darker) and 95\% (lighter) probability when marginalising
    over non-zero $\mbox{Re}(\wilson[NP]{10}) \in [-1,\, 9]$ as well as and
    $\mbox{Im}(\wilson[NP]{10})$ and $\mbox{Re, Im}(\wilson[NP]{10'}) \in [-5,\,5]$.
    For comparison the according constraints from all data when keeping
    $\mbox{Re, Im}(\wilson[NP]{10,\, 10'}) = 0$ (red)
    at 68\% (darker) and 95\% (lighter) probability.
    }
  }
  \label{fig:scalar:SM-EFT}
\end{figure*}

@@

The SM gauge groups do not impose constraints on the operators of the SM-EFT that
imply relations among $\wilson{10}$ and $\wilson{10'}$, so they
are in general additional independent parameters. Here we find that destructive
interference with contributions involving $\wilson{10,\, 10'}$ do not change
much upper bounds on $|\wilson{S,\, S'}|$ found in \cite{Alonso:2014csa}. However,
for the most general case of complex-valued couplings destructive interference
constrains (4 parameters) \todo{finish, describe \reffig{fig:scalar:SM-EFT}}

@@

Here we describe the theoretical treatment of observables and collect numerical
input of the most relevant parameters. The software package {\tt EOS} \cite{Bobeth:2011gi,
Bobeth:2011nj, EOS} is used for predictions of observables in $B_s\to \bar\mu\mu$
and $B\to K^{(*)}\bar\ell\ell$. The fit is performed with the package {\tt pypmc},
which incorporates the algorithm presented in \cite{Beaujean:2013:PMC, Beaujean:2012uj}
and in addition an implementation of the variational Bayes algorithm.

>>>>

\begin{figure*}
  \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_0,2}
  \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_1,3}
  \caption{
    Constraints (2D-marginalized) on complex-valued scalar couplings 
    $\wilson{S,\,S'}$ in the scenario SM-EFT from all data in 
    \reftab{tab:observables} (red) at 68\% (darker) and 95\% 
    (lighter) probability when marginalising over non-zero $\mbox{Re, Im}
    (\wilson[NP]{10,\,10'}) \in [-7,\,7]$.
    For comparison the according constraints from only $\overline{\cal B}(B_s\to \bar\mu\mu)$
    and $F_H^\mu$ \todo{What else?}
    (dashed blue contours) at 68\% (inner) and 95\% (outer) probability.
  }
  \label{fig:scalar:SM-EFT}
\end{figure*}

@@

The SM gauge groups do not impose constraints on the operators of the SM-EFT that
imply relations among $\wilson{10}$ and $\wilson{10'}$, so they
are in general additional independent parameters. Here we find that destructive
interference with contributions involving $\wilson{10,\, 10'}$ do not change
much upper bounds on $|\wilson{S,\, S'}|$ found in \cite{Alonso:2014csa}. Since we
consider here complex-valued couplings the allowed regions are circles rather
than rings as for the case of real-valued couplings. The result of the simultaneous
fit of complex-valued $\wilson{S,\,S',\,10,\,10'}$ is shown in 
\reffig{fig:scalar:SM-EFT}.

@@

Here we describe the theoretical treatment of observables and collect
numerical input of the most relevant parameters. The software package
{\tt EOS} \cite{Bobeth:2011gi, Bobeth:2011nj, EOS} is used for
predictions of observables in $B_s\to \bar\mu\mu$ and $B\to
K^{(*)}\bar\ell\ell$. The fit is performed with the package {\tt
  pypmc}, which incorporates the algorithm presented in
\cite{Beaujean:2013:PMC, Beaujean:2012uj} and in addition an
implementation of the variational Bayes algorithm. \fred{Add, get DOI
  for pypmc version}
